Some usefull words/expressions/sentences

### 2018-07-18 paper/Chapters/Chapter2.tex
some methods updated

To produce a sequence of discrete responses about the carbohydrate intake we are interested, we calculated the energy consumption per hour for each participant. The percentage of energy that contributed by carbohydrate within each hour were calculated for every every participant, each single day. Since we planed to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical. We then dichotomised the responses according to the carbohydrate contribution to the energy intake at cut-off value of 50\%, i.e. if within an hour if there is any energy intake occured, carbohydrate consumption was categorised into whether it's energy contribution was higher or equal to 50\% of total energy. Consequently, for each day of the recording, there were 24 data points generated by the dairy.

@@

>>>>

To produce a sequence of discrete responses about the carbohydrate intake we are interested, we calculated the energy consumption per hour for each participant. The percentage of energy that contributed by carbohydrate within each hour were calculated for every every participant, each single day. Since we planed to apply latent class analysis (LCA) in the current study, in which the observed indicators for latent classes must be categorical, we then dichotomised the responses according to the carbohydrate contribution to the energy intake at cut-off value of 50\%, i.e. if within an hour if there is any energy intake occured, carbohydrate consumption was categorised into whether it's energy contribution was higher or equal to 50\% of total energy. Consequently, for each day of the recording, there were 24 data points generated by the dairy, each data point included one of the following responses:

\begin{itemize}
	\item Not eating; 
	\item Eating, and carbohydrate contributed less than 50\% of the total energy intake;
	\item Eating, and carbohydrate contributed higher or equal to 50\% of the total energy intake.
\end{itemize}

@@

The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Akaike information criterion (AIC), Bayesian information criterion (BIC), adjusted Bayesian information criterion (aBIC) where smaller values indicate better, and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} and the Bootstrap Likelihood ratio test (BS-LRT) \parencite{peel2000robust} which compare $q$ vs. $q-1$ class models, where $q$ is the number of latent classes and 3) pattern interpretability. In the step of performing multilevel LCA, where neither LMR-LRT nor BS-LRT were available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2.

### 2018-07-18 phrases.Rmd
some methods updated

>>>>

## hashimoto2018intake - Intake of Carbohydrate to Fiber Ratio Is a Useful Marker for Metabolic Syndrome in Patients with Type 2 Diabetes: A Cross-Sectional Study

- Recent studies revealed that low carbohydrate diet (LCD) is useful for weight reduction [4, 5]. However,
whether LCD is useful for human health, including all causes and cardiovascular disease mortality, or not is still
controversial [6–8].

## alessa2018carbohydrate - Carbohydrate quality and quantity and risk of coronary heart disease among US women and men

- Compared with total carbohydrates, saturated fat intake was not significantly associated with CHD or cardiovascu-
lar disease outcomes (10).
